Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-30 Ben_Manuscripts/transport/Draft.tex
Updates
Text fixes and updates to errorbars

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. 
%  These membranes have been primarily characterized with size-exclusion experiments
%  which can give an estimate of pore size as well as selectivity based on differences
%  in solute sizes~\cite{zhou_supported_2005}.  
  The separation performance of these membranes has been 
  primarily characterized with size-exclusion experiments which emphasizes 
  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
  %separation BY size exclusion; maybe rephrase?
  %BJC4: Hmm, by characerization, I mean testing their ability to separate, so I'm 
  While size-exclusion is a useful separation, it 
  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
  important to take advantage of material properties other than pore size. 
  Unfortunately, this is a more complicated design problem. Experimental transport
  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
  unclear trends due to interactions between solutes and pore moieties. Although
  the authors identified some correlation between select physicochemical properties
  and solute transport trends, their empirical model does not offer a sufficient 
  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
  %MRS4: expand the above.  What was discovered, and why was it unfortuate to the thesis?  
  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?
  %BJC4: gave it another shot above.

@@

  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order to avoid studying charge species, we have only studied
  %BJC: citations for pKa's
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75. Assuming that the pKa of gallic acid is similar 
  to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
  same time as protonated acetic acid. In any case, we are more interested 
  in mechanisms of interaction with specific chemical functionality more than 
  the behavior of specific molecules.

%MRS4: probably shouldn't capitalize the names.  Maybe make the yellow a bit darker for the text.
%BJC4: tried a new yellow. I think it's more readable. Hard to say

  \begin{table}[h!]
  \centering
%  \begin{minipage}{.4\textwidth}
%  \tiny
%  \begin{tabular}{ |lcc|lcc| }
  \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
    \hline
    \multicolumn{2}{|c}{Solute Name~~~~~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
    \hline
	\color{blue}{methanol} & \color{blue}{MeOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/MET.pdf}
    \end{minipage} &

    \color{green!40!olive}{urea} & \color{green!40!olive}{URE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/URE.pdf}
    \end{minipage} \\

   	\color{blue}{ethanol} & \color{blue}{EtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ETH.pdf}
    \end{minipage} &

    \color{green!40!olive}{acetamide} & \color{green!40!olive}{AcN} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ACN.pdf}
    \end{minipage} \\

  	\color{blue}{propanol} & \color{blue}{PrOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PR.pdf}
    \end{minipage} &

    \color{green!40!olive}{acetone} & \color{green!40!olive}{ACE} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ATO.pdf}
    \end{minipage} \\

    \color{blue}{butanol} & \color{blue}{BtOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/BUT.pdf}
    \end{minipage} &

    \color{orange}{mercaptoethanol} & \color{orange}{ME} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/SOH.pdf}
    \end{minipage} \\

    \color{red}{ethylene glycol} & \color{red}{EG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/GCL.pdf}
    \end{minipage} &

    \color{orange}{dimethyl sulfoxide} & \color{orange}{DMSO} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMS.pdf}
    \end{minipage} \\

    \color{red}{propylene glycol} & \color{red}{PG} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PG.pdf}
    \end{minipage} &

    \color{orange}{2,3-dimercapto-1-propanol} & \color{orange}{DMP} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMP.pdf}
    \end{minipage} \\

    \color{red}{glycerol} & \color{red}{GLY} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/GLY.pdf}
    \end{minipage} &

    \color{amber}{tetrahydrofuran} & \color{amber}{THF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/THF.pdf}
    \end{minipage} \\

    \color{red}{tetrose} & \color{red}{TET} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/TET.pdf}
    \end{minipage} &

    \color{amber}{dimethylformamide} & \color{amber}{DMF} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMF.pdf}
    \end{minipage} \\

    \color{red}{ribose} & \color{red}{RIB} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/RIB.pdf}
    \end{minipage} &

    \color{amber}{propylene carbonate} & \color{amber}{PC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PCB.pdf}
    \end{minipage} \\

    \color{green!40!olive}{acetic acid} & \color{green!40!olive}{AcOH} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ACH.pdf}
    \end{minipage} &

    \color{amber}{ethyl acetate} & \color{amber}{EAC} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/EAC.pdf}
    \end{minipage} \\

    \hline
  \end{tabular}
%  \end{minipage}
  \caption{Names of solutes along with their molecular structures and the
  abbreviations which we use in this paper. Colors corresponds to solute groupings
  and are used in many plots. Blue corresponds to simple alcohols, red to 
  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.}\label{table:abbreviations}
  % BJC: achemso for jpcb makes table captions bold
  % BJC: also, it's published that way
  \end{table}

@@

  We first address the structure of the pores formed in the membrane.
  Previously, we have studied dry membrane systems and some systems with 
  low water content. We 
  %MRS4: we already observed it
  %will observe 
  therefore first analyze 
  how the radial density of monomer 
  components and water change within the pore based on membrane water content.

  We then present our efforts to understand how small molecules, 
  including water, partition within the pores. From a macroscopic perspective,
  %MRS4: tweak.
  %it is straightforward 
  it might make sense
  to hypothesize that the water and polar solutes spend
  their time exclusively in the tube-like hydrophilic pore region. 
  %MRS4: However,
  our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. We then study the gradient in composition of solutes and 
  water and any resultant influence it might have on mechanistic properties.

  %MRS4:
  %For 
  In
  the remainder of the paper, we present our observations 
  and explanations of the observed transport mechanisms exhibited by water
  and solutes. Given that the pores will restrict motion of the solutes, we
  anticipate that transport will be hindered in some way.

@@

  There are also a couple of 
  %points 
  questions
  that this study 
  % is not intended to address. 
  that are beyond the scope of this study.
  First, we will not study the concentration dependence of the observed transport
  rates. Although the average MSD might change with concentration, we are 
  focused on the underlying solute-membrane interactions that lead to the 
  observed transport mechanisms which we conjecture will 
  %MRS4: Some tone tweaks below.
  %be 
  remain roughly
  the same 
  regardless of concentration. Second, we will not study the chemical potential
  of solutes in the pores, which could give us a better understanding of 
  equilibrium solute partitioning. However, this information 
  %will not greatly enhance our
  is not needed to 
  understanding of mechanistic details in various membrane regions; 
  %Both of the
  %above points will add unnecessary levels of complexity which can be left for
  %a future study. 
  this work 
  %is a simple 
  represents
  starting point for observing
  the types of interactions which occur between isolated solutes and the
  membrane.

@@

  We observed that 
  %MRS4: added
  some
  water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition. We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region.

@@

  To study a given solute, we added 6, equally spaced in $z$, solute molecules to the
  center of each pore of the equilibrated cross-linked configuration. Our choice of 6
  solutes per pore provided a balance of a useful amount of data for generating 
  statistics and a low degree of interaction between solutes (see 
  Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
  insertion point we placed a randomly oriented solute molecule then ran a short 
  energy minimization. We allowed the solutes to equilibrate for 5 ns using Berendsen
  pressure control then collected transport data over the course of 1 $\mu$s MD simulations.
  %MRS4: Was Berendsen pressure control used for the transport as well?  Should specify?  I thought those might have been NVT? If so, should put in an acknowledgement that it's not quite right, cite my and Pascal's paper.
  \subsection{Solute Parameterization}\label{method:parameterization}

  We parameterized the interaction potential for the monomer and solutes using 
  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
  We use GAFF 
  as it has been used extensively 
  %since it has been parameterized 
  for use with organic molecules.
  We
  assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
  with QUACPAC from Openeye Scientific Software.

@@

  We measured the time-averaged $z$-direction mean squared displacement (MSD) of the
  centers of mass (COM) of each solute over the course of 1 $\mu$s MD simulations using 
  Equation~\ref{eqn:tamsd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:tamsd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  %Generally, 
  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
    % fully understand the theory since I talk about subdiffusion in terms of 
    % alpha which is always calculated based on ensemble MSD unless we know for sure that
    % the system is ergodic (which it isn't the case for CTRW)
  In practice, $\alpha$ corresponds to the growth of the \textit{ensemble} MSD given
  by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
  \begin{equation}
	\langle z^2(t) \rangle = \langle z(t) - z(0) \rangle
	\label{eqn:ensemble_msd}
  \end{equation}
  Since the ensemble MSD is calculated with respect to a reference position, it carries
  some dependence on its starting point. The time-averaged MSD averages over all possible
  time lags of a given length, effectively eliminating any initial configuration 
  dependence and generating	an increased number of observations. For ergodic systems, 
  both types of MSDs will be equal. Since we have a small number of solutes with which to
  generate statistics and because we are not calculating values of $\alpha$ for this 
  particular study,	we will only use the time-averaged MSD.

@@

  The $z$-direction MSD of water in the 10 wt\% system is linear. Therefore, for
  the purpose of comparison, we calculated its diffusion constant by fitting a line
  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured 
  %MRS4: check that this change is correct. 
  %the diffusion coefficient 
  particle displacement
  in one dimension.

@@

  The Stokes-Einstein relationship expresses the diffusion coefficient of 
  a hard spherical particle as a function that is inversely related to the
  particle's radius:
  \begin{equation}
  D = \dfrac{k_bT}{6\pi\eta fr}
  \label{eqn:stokes-einstein}
  \end{equation}
  where $k_b$ and $T$ are the Boltzmann	constant and the system temperature
  respectively and $\eta$ is the system's viscosity. Here we have also 
  included the microfriction correction factor, $f$, introduced by 
  Gierer and Wirtz~\cite{gierer_molekulare_1953,chen_diffusion_1984} for when
  solute size becomes on the order of solvent size since the solute can no 
  longer be treated as a non-interacting hard sphere. $f$ is defined in terms
  of the ratio of $r_1$ and $r_2$, the radii of the solute and solvent molecules
  respectively:
  \begin{equation}
  f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}
  %f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}
  \label{eqn:correction_factor}
  \end{equation}
  For consistency with the presentation of our results, rather than calculate trends
  in $D$, we will apply Equation~\ref{eqn:stokes-einstein} in order to analyze 
  trends in solute MSDs, which is only valid because all trajectories are of the 
  %MRS4: a bit strange to say you are using Stokes-einstein, but only analyzing MSD's (when MSD's don't appear in that equation)? It could be clarified a bit more.
  same length.
%  However, this assumes linear behavior
%  of the MSD, which we will show is not that case. Our main usage of the 
%  Stokes-Einstein relationship is to show that solutes in our system do not 
%  behave as it predicts.
  % Possible comps question: Stokes law restricted to Re < 0.1, but we have no flow so Re ~ 0.

  Since we will be using this equation for primarily qualitative observations, 
  we made a number of simplifying assumptions so that it could easily be used for 
  comparison between systems. First, we assume that all systems' viscosities
  are equal since we only make minor changes to the membrane's composition and
  accurately assessing the viscosity in a complex and inhomogeneous system such 
  as ours is a challenge by itself. Second, we assume all particles are approximately
  spherical, neglecting the effect of solute shape on mobility. Chan et al. 
  showed that the difference in diffusion constants of differently shaped 
  particles, with constant molecular volume, did not differ by more than 25\%
  with most deviating by less than 10\%.~\cite{chan_effects_2015}. 
  Third, we assume that the ratio of solute and solvent radii as calculated using the
  methodology of Section~\ref{method:molecular_size}, is equivalent to the the 
  ratio of hydrodynamic radii. For similarly shaped molecules, it has been shown that
  one can relate the hydrodynamic radius and radius of gyration (R\textsubscript{g})
  using a constant scaling factor. \cite{lee_molecular_2008,he_novel_2003,li_critical_2009}.
  % BJC: could just calculate Rg instead of end-to-end
  Assuming that our end-to-end distance reasonably approximates R\textsubscript{g} 
  for our small, relatively inflexible molecules, we believe this assumption is 
  justified for qualitative demonstrations relevant to this study.

>>>>

  While H\textsubscript{II} membranes have been synthesized and characterized
  in a lab setting, there is a limit to the level of detail that can be obtained 
  from experiment. These membranes have been primarily characterized with 
  size-exclusion experiments which can give an estimate of pore size as well as
  selectivity based on differences in solute sizes~\cite{zhou_supported_2005}. 
  However, size exclusion does not appear to be sufficient to fully describe LLC
  membranes. Dischinger et al. studied a similar membrane and found that they do
  not separate purely on the basis of size. Empirical modeling revealed correlations
  between various solute physicochemical properties and observed solute rejection. 
  Although there was some agreement with their empirical model, it does not
  offer a sufficiently detailed explanation of governing molecular interactions.
  ~\cite{dischinger_effect_2017}

%  The separation performance of these membranes has been 
%  primarily characterized with size-exclusion experiments which emphasizes 
%  selectivity based on the ability to enter a given pore.~\cite{zhou_supported_2005}
%  %MRS4: might confuse readers here - talking about both size exclusion as a method to characterize the membranes, and 
%  %separation BY size exclusion; maybe rephrase?
%  %BJC4: Hmm, by characerization, I mean testing their ability to separate, so I'm 
%  While size-exclusion is a useful separation, it 
%  cannot reliably purify a solution where the solute size is on the same order as water. Therefore, it is
%  important to take advantage of material properties other than pore size. 
%  Unfortunately, this is a more complicated design problem. Experimental transport
%  studies of small solutes in a Q\textsubscript{I} phase membrane yielded 
%  unclear trends due to interactions between solutes and pore moieties. Although
%  the authors identified some correlation between select physicochemical properties
%  and solute transport trends, their empirical model does not offer a sufficient 
%  explanation of the molecular interactions responsible for those correlations~\cite{dischinger_effect_2017}
  %MRS4: expand the above.  What was discovered, and why was it unfortuate to the thesis?  
  % I though it actually helped the thesis here since there was something happening that WASN'T just size dependence?

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ortho_view.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{top_view.pdf}
  \caption{}
  \end{subfigure}
  \caption{In both figures, water molecules that occupy the pores are colored blue,
  the hydrophilic head groups of the LLC monomers are colored orange with all else
  colored gray. (a) Membrane pores are approximately straight and (b) are packed 
  hexagonally.}\label{fig:membrane_rendering}
  \end{figure}

  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of
  the membrane in which solutes are placed. 
  We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order to avoid studying charge species, we have only studied
  %BJC: citations for pKa's
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75. Assuming that the pKa of gallic acid is similar 
  to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
  same time as protonated acetic acid. In any case, we are more interested 
  in mechanisms of interaction with specific chemical functionality more than 
  the behavior of specific molecules.

  \begin{table}[h!]
  \centering
%  \begin{minipage}{.4\textwidth}
%  \tiny
%  \begin{tabular}{ |lcc|lcc| }
  \begin{tabular}{ |m{3.5cm}m{1.4cm}m{2cm}|m{3.8cm}m{1.4cm}m{2cm}| }
    \hline
    \multicolumn{2}{|c}{Solute Name~~~~~~~~~Abbreviation} & Structure &\multicolumn{2}{c}{Solute Name~~~~~~~~~Abbreviation} & Structure \\
    \hline
	\color{blue}{\textbf{methanol}} & \color{blue}{\textbf{MeOH}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/MET.pdf}
    \end{minipage} &

    \color{green!40!olive}{\textbf{urea}} & \color{green!40!olive}{\textbf{URE}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/URE.pdf}
    \end{minipage} \\

   	\color{blue}{\textbf{ethanol}} & \color{blue}{\textbf{EtOH}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ETH.pdf}
    \end{minipage} &

    \color{green!40!olive}{\textbf{acetamide}} & \color{green!40!olive}{\textbf{AcN}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ACN.pdf}
    \end{minipage} \\

  	\color{blue}{\textbf{propanol}} & \color{blue}{\textbf{PrOH}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PR.pdf}
    \end{minipage} &

    \color{green!40!olive}{\textbf{acetone}} & \color{green!40!olive}{\textbf{ACE}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ATO.pdf}
    \end{minipage} \\

    \color{blue}{\textbf{butanol}} & \color{blue}{\textbf{BtOH}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/BUT.pdf}
    \end{minipage} &

    \color{orange}{\textbf{mercaptoethanol}} & \color{orange}{\textbf{ME}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/SOH.pdf}
    \end{minipage} \\

    \color{red}{\textbf{ethylene glycol}} & \color{red}{\textbf{EG}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/GCL.pdf}
    \end{minipage} &

    \color{orange}{\textbf{dimethyl sulfoxide}} & \color{orange}{\textbf{DMSO}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMS.pdf}
    \end{minipage} \\

    \color{red}{\textbf{propylene glycol}} & \color{red}{\textbf{PG}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PG.pdf}
    \end{minipage} &

    \color{orange}{\textbf{2,3-dimercapto-1-propanol}} & \color{orange}{\textbf{DMP}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMP.pdf}
    \end{minipage} \\

    \color{red}{\textbf{glycerol}} & \color{red}{\textbf{GLY}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/GLY.pdf}
    \end{minipage} &

    \color{amber}{\textbf{tetrahydrofuran}} & \color{amber}{\textbf{THF}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/THF.pdf}
    \end{minipage} \\

    \color{red}{\textbf{tetrose}} & \color{red}{\textbf{TET}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/TET.pdf}
    \end{minipage} &

    \color{amber}{\textbf{dimethylformamide}} & \color{amber}{\textbf{DMF}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/DMF.pdf}
    \end{minipage} \\

    \color{red}{\textbf{ribose}} & \color{red}{\textbf{RIB}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/RIB.pdf}
    \end{minipage} &

    \color{amber}{\textbf{propylene carbonate}} & \color{amber}{\textbf{PC}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/PCB.pdf}
    \end{minipage} \\

    \color{green!40!olive}{\textbf{acetic acid}} & \color{green!40!olive}{\textbf{AcOH}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/ACH.pdf}
    \end{minipage} &

    \color{amber}{\textbf{ethyl acetate}} & \color{amber}{\textbf{EAC}} &     
    \begin{minipage}{.1\textwidth}
    \includegraphics[width=\linewidth]{structures/EAC.pdf}
    \end{minipage} \\

    \hline
  \end{tabular}
%  \end{minipage}
  \caption{Names of solutes along with their molecular structures and the
  abbreviations which we use in this paper. Colors corresponds to solute groupings
  and are used in many plots. Blue corresponds to simple alcohols, red to 
  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.}\label{table:abbreviations}
  \end{table}

@@

  We first address the structure of the pores formed in the membrane.
  Previously, we have studied dry membrane systems and some systems with 
  low water content. We therefore first analyze how the radial density of monomer 
  components and water change within the pore based on membrane water content.

  We then present our efforts to understand how small molecules, 
  including water, partition within the pores. From a macroscopic perspective,
  it might make sense to hypothesize that the water and polar solutes spend
  their time exclusively in the tube-like hydrophilic pore region. Our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. We then study the gradient in composition of solutes and 
  water and any resultant influence it might have on mechanistic properties.

  In the remainder of the paper, we present our observations 
  and explanations of the observed transport mechanisms exhibited by water
  and solutes. Given that the pores will restrict motion of the solutes, we
  anticipate that transport will be hindered in some way.

@@

  There are also a couple of questions that this study that are beyond the 
  scope of this study. First, we will not study the concentration dependence of the observed transport
  rates. Although the average MSD might change with concentration, we are 
  focused on the underlying solute-membrane interactions that lead to the 
  observed transport mechanisms which we conjecture will remain roughly
  the same regardless of concentration. Second, we will not study the chemical potential
  of solutes in the pores, which could give us a better understanding of 
  equilibrium solute partitioning. However, this information is not needed
  to understand the mechanistic details in various membrane regions; 
  This work represents a starting point for observing the types of interactions
  which occur between isolated solutes and the membrane.

@@

  We observed that some water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition. We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region.

@@

  To study a given solute, we added 6, equally spaced in $z$, solute molecules to the
  center of each pore of the equilibrated cross-linked configuration. Our choice of 6
  solutes per pore provided a balance of a useful amount of data for generating 
  statistics and a low degree of interaction between solutes (see 
  Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
  insertion point we placed a randomly oriented solute molecule then ran a short 
  energy minimization. We allowed the solutes to equilibrate for 5 ns using Berendsen
  pressure control then collected transport data over the course of 1 $\mu$s MD simulations
  with pressure controlled by the Parrinello-Rahman barostat.

  \subsection{Solute Parameterization}\label{method:parameterization}

  We parameterized the interaction potential for the monomer and solutes using 
  the Generalized AMBER Force Field (GAFF)~\cite{wang_development_2004} with the
  Antechamber package \cite{wang_automatic_2006} shipped with AmberTools16~\cite{case_ambertools16_2016}.
  We use GAFF as it has been used extensively for use with organic molecules.
  We assigned atomic charges using the am1bccsym method of \texttt{molcharge} included
  with QUACPAC from Openeye Scientific Software.

@@

  We measured the time-averaged $z$-direction mean squared displacement (MSD) of the
  centers of mass (COM) of each solute over the course of 1 $\mu$s MD simulations using 
  Equation~\ref{eqn:tamsd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:tamsd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
    % fully understand the theory since I talk about subdiffusion in terms of 
    % alpha which is always calculated based on ensemble MSD unless we know for sure that
    % the system is ergodic (which it isn't the case for CTRW)
  In practice, $\alpha$ corresponds to the growth of the \textit{ensemble} MSD given
  by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
  \begin{equation}
	\langle z^2(t) \rangle = \langle z(t) - z(0) \rangle
	\label{eqn:ensemble_msd}
  \end{equation}
  Since the ensemble MSD is calculated with respect to a reference position, it carries
  some dependence on its starting point. The time-averaged MSD averages over all possible
  time lags of a given length, effectively eliminating any initial configuration 
  dependence and generating	an increased number of observations. For ergodic systems, 
  both types of MSDs will be equal. Since we have a small number of solutes with which to
  generate statistics and because we are not calculating values of $\alpha$ for this 
  particular study,	we will only use the time-averaged MSD.

@@

  The $z$-direction MSD of water in the 10 wt\% system is linear. Therefore, for
  the purpose of comparison, we calculated its diffusion constant by fitting a line
  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured particle displacement in one dimension.

@@

  The Stokes-Einstein relationship expresses the diffusion coefficient of 
  a hard spherical particle as a function that is inversely related to the
  particle's radius:
  \begin{equation}
  D = \dfrac{k_bT}{6\pi\eta fr}
  \label{eqn:stokes-einstein}
  \end{equation}
  where $k_b$ and $T$ are the Boltzmann	constant and the system temperature
  respectively and $\eta$ is the system's viscosity. Here we have also 
  included the microfriction correction factor, $f$, introduced by 
  Gierer and Wirtz~\cite{gierer_molekulare_1953,chen_diffusion_1984} for when
  solute size becomes on the order of solvent size since the solute can no 
  longer be treated as a non-interacting hard sphere. $f$ is defined in terms
  of the ratio of $r_1$ and $r_2$, the radii of the solute and solvent molecules
  respectively:
  \begin{equation}
  f = \left(1.5\dfrac{r_2}{r_1} + \dfrac{1}{1 + \dfrac{r_2}{r_1}}\right)^{-1}
  %f = \left(1.5(r_2/r_1) + \dfrac{1}{1 + (r_2/r_1)}\right)^{-1}
  \label{eqn:correction_factor}
  \end{equation}
  For consistency with the presentation of our results, rather than calculate 
  trends in $D$, we will calculate trends in trends in solute MSDs. For Brownian
  particles, $D$ is proportional to the MSD divided by time, $t$. Therefore, 
  we analyze qualitative trends in solute MSDs according to:
  \begin{equation}
  MSD = \dfrac{k_bTt}{6\pi\eta fr}
  \label{eqn:msd-stokes-einstein}
  \end{equation}
  We hold $t$ constant in our simulations in order to make side-by-side comparisons.

  %MRS4: a bit strange to say you are using Stokes-einstein, but only analyzing MSD's (when MSD's don't appear in that equation)? It could be clarified a bit more.
%  However, this assumes linear behavior
%  of the MSD, which we will show is not that case. Our main usage of the 
%  Stokes-Einstein relationship is to show that solutes in our system do not 
%  behave as it predicts.
  % Possible comps question: Stokes law restricted to Re < 0.1, but we have no flow so Re ~ 0.
